Comparing Apples and Oranges in Youth Depression Treatments?

### 2024-09-23 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
changed dimensions for plots for word

list_df_simulated[[1]] %>%
  filter(arm_effect_size == "cohens_d_control") %>%
  ggplot(aes(x = cohens_d, y = 0, color = as.factor(psy_or_med), size = baseline_n)) +
  geom_jitter(height = 0.2, alpha = 0.7) +
  geom_point(alpha = 0.7) +
  labs(
    x = "SMD",
    y = "",
    color = "Type of Study",
    size = "Baseline n"
  ) +
  scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  )

@@

 png("plot_means_multi_all.png")
 plot_means_multi_all
 dev.off()

@@

print(mean_diff_min_max_scores) 
png("mean_diff_min_max_scores.png")
mean_diff_min_max_scores
dev.off()
```

@@

print(plot_baseline_var)
png("plot_baseline_var.png")
plot_baseline_var
dev.off()
```

@@

 png("plot_means_multi_no_wl.png")
plot_means_no_wl
 dev.off()

@@

png("plot_means_multi_clin.png")
plot_means_clin
dev.off()

@@

 png("plot_means_multi_cdrs.png")
 plot_means_cdrs
 dev.off()

@@

 png("plot_means_multi_hamd.png")
 plot_means_multi_hamd
 dev.off()

@@

 png("plot_means_multi_sd.png")
 plot_means_multi_sd
 dev.off()
```

@@

 png("plot_means_multi_var2.png")
 plot_means_multi_var2
 dev.off()
```

>>>>

plot_smd_diff_control <- list_df_simulated[[1]] %>%
  filter(arm_effect_size == "cohens_d_control") %>%
  ggplot(aes(x = cohens_d, y = 0, color = as.factor(psy_or_med), size = baseline_n)) +
  geom_jitter(height = 0.2, alpha = 0.7) +
  geom_point(alpha = 0.7) +
  labs(
    x = "SMD",
    y = "",
    color = "Type of Study",
    size = "Baseline n"
  ) +
  scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  )

print(plot_smd_diff_control)

png("plot_smd_diff_control.png", width=6.5, height=4, units="in", res=300)
 plot_smd_diff_control
 dev.off()

@@

 png("plot_means_multi_all.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_all
 dev.off()

@@

print(mean_diff_min_max_scores) 
png("mean_diff_min_max_scores.png", width=6.5, height=4, units="in", res=300)
mean_diff_min_max_scores
dev.off()
```

@@

print(plot_baseline_var)
png("plot_baseline_var.png", width=6.5, height=4, units="in", res=300)
plot_baseline_var
dev.off()
```

@@

 png("plot_means_multi_no_wl.png", width=6.5, height=4, units="in", res=300)
plot_means_no_wl
 dev.off()

@@

png("plot_means_multi_clin.png", width=6.5, height=4, units="in", res=300)
plot_means_clin
dev.off()

@@

 png("plot_means_multi_cdrs.png", width=6.5, height=4, units="in", res=300)
 plot_means_cdrs
 dev.off()

@@

 png("plot_means_multi_hamd.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_hamd
 dev.off()

@@

 png("plot_means_multi_sd.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_sd
 dev.off()
```

@@

 png("plot_means_multi_var2.png", width=6.5, height=4, units="in", res=300)
 plot_means_multi_var2
 dev.off()
```
